---
title: "Multivariate"
output: 
  html_document: 
    keep_md: yes
---

Import necessary libraries and data sets
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
library(dplyr) 
library(tidyr)
library(reshape2)
library(GGally)
```

Setting seed for reproducibility
```{r}
set.seed(1234)
```

Load pseudo facebook data set
```{r}
destfile <- "input/pseudo_facebook.tsv"

if(!file.exists(destfile)){
  download.file("https://s3.amazonaws.com/udacity-hosted-downloads/ud651/pseudo_facebook.tsv",destfile=destfile,method="libcurl")
}
pseudo_facebook <- read.csv(file=destfile, sep="\t")
```

New dataframe arranged by age and gender
```{r}
pf.fc_by_age_gender <- pseudo_facebook %>%
  subset(!is.na(gender)) %>%
  group_by(age, gender) %>% 
  summarise(mean_friend_count = mean(friend_count)
            , median_friend_count = median(friend_count)
            , n = n()) %>%
  arrange(age, gender)
```

Line plot of median friend count by age split by gender - Females have a greater friend count until ~65 year of age
```{r}
ggplot(data = pf.fc_by_age_gender, aes(x = age, y = median_friend_count, color = gender)) + geom_line()
```

Line plot of female over male ratio of median friend count - Females have up to 2.5 times more friend than males in younger ages.

```{r}
pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender, 
                                  age ~ gender,
                                  value.var = "median_friend_count")
ggplot(data = pf.fc_by_age_gender.wide, aes(x = age, y = (female/male))) + 
  geom_line() +
  geom_hline(yintercept = 1, alpha = 0.3, linetype = 2)
```

```{r}
pseudo_facebook$years_joined <- floor(2014 - (pseudo_facebook$tenure/365))
pseudo_facebook$years_joined.bucket <- cut(pseudo_facebook$years_joined, c(2004, 2009, 2011, 2012, 2014))
```

Line plot of mean friend count by age split by gender (Including grand mean)
```{r}
ggplot(aes(x = age, y = friend_count), 
              data = subset(pseudo_facebook, !is.na(gender) & !is.na(years_joined.bucket))) + 
  geom_line(aes(color = years_joined.bucket), stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = mean, linetype = 2)
```

Summary of the friend count per tenure days 
```{r}
with(subset(pseudo_facebook, tenure >= 1), summary(friend_count/tenure))
```

Line plot of mean friendships initiated by tenure coloured by year joined groups
```{r}
ggplot(data=subset(pseudo_facebook, tenure >= 1), aes(x=tenure, y=friendships_initiated/tenure)) +
  geom_line(aes(color=years_joined.bucket), stat='summary', fun.y=mean)
```

Smoothened line plot of mean friendships initiated by tenure coloured by year joined groups
```{r message=FALSE, warning=FALSE}
ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pseudo_facebook, tenure > 0)) +
  geom_smooth(aes(color = years_joined.bucket))
```

Explore yogurt dataset
```{r message=FALSE, warning=FALSE}
yo <- read.csv("input/yogurt.csv")
yo$id <- as.factor(yo$id) 
head(yo)
summary(yo)
ggplot(data=yo, aes(x=price)) + geom_histogram()
```

Create a total purchases variable per household
```{r}
yo <- transform(yo, all.purchases=strawberry+blueberry+pina.colada+plain+mixed.berry)
```

Distribution of total purchases
```{r message=FALSE, warning=FALSE}
ggplot(data=yo, aes(x=all.purchases)) + geom_histogram()
```

```{r}
ggplot(data=yo, aes(x=time, y=price)) + geom_point() + geom_jitter(alpha=1/4, shape=21)
```

```{r}
sample.ids <- sample(levels(yo$id), 16)

ggplot(data=subset(yo, id %in% sample.ids), 
       aes(x=time, y=price)) +
  geom_line() +
  geom_point(aes(size=all.purchases), pch=1) +
  facet_wrap(~id)
```

```{r message=FALSE, warning=FALSE}
theme_set(theme_grey(base_size=5))
pf_subset = pseudo_facebook[, c('age', 'dob_year', 'dob_month', 'gender', 'tenure')]
ggpairs(pf_subset[sample.int(nrow(pf_subset), 1000), ], axisLabels = "internal")
```

