---
title: "One Variable"
output: 
  html_document: 
    keep_md: yes
---

Import necessary libraries
```{r}
library("ggplot2")
library(gridExtra)
```

Load pseudo facebook data set
```{r}
pf_data_link <- "https://s3.amazonaws.com/udacity-hosted-downloads/ud651/pseudo_facebook.tsv"
pseudo_facebook <- read.csv(file=pf_data_link, sep="\t")
```

Visualize data set structure and sample
```{r, echo=FALSE}
str(pseudo_facebook)
head(pseudo_facebook)
```

Friend counts histogram faceted by gender
```{r, echo=FALSE}
qplot(x = friend_count, data = subset(pseudo_facebook, !is.na(gender)), binwidth = 25
      , color = I('black'), fill = I('blue')) +
  xlab("Number of friends") +
  ylab("Number of users") +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 100)) +
  facet_wrap(~gender)
```

Friend count statistics by gender
```{r}
by(pseudo_facebook$friend_count, pseudo_facebook$gender, summary)
```

Tenure histogram in years
```{r, echo=FALSE}
qplot(x = (tenure/365), data = pseudo_facebook, binwidth = .25 
      , color = I('black'), fill = I('blue')) +
  xlab("Number of years using facebook") +
  ylab("Number of users") +
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7))
```

User's age histogram
```{r, echo=FALSE}
qplot(x=age, data=pseudo_facebook, binwidth=1
      , color = I('black'), fill = I('blue')) +
  xlab("User's age") +
  ylab("Number of users") +
  scale_x_continuous(breaks=seq(0, 150, 5)) +
  scale_y_continuous(breaks=seq(0, 6000, 500))
```

Three different friend's count histograms: 1) Count, 2) Base 10 log transformation of count, and 3) Square root transformation of count 
```{r, echo=FALSE}
fc <- qplot(x = friend_count, data = pseudo_facebook, binwidth=25
            , color = I('black'), fill = I('blue')) +
  xlab('Number of friends') +
  ylab('Number of users') +
  scale_x_continuous(breaks=seq(0, 5000, 100), limits=c(0, 2500))

fc_log10 <- qplot(x = friend_count+1, data = pseudo_facebook, binwidth=.05
                  , color = I('black'), fill = I('blue')) +
  xlab('Number of friends (Base 10 logarithm transformation)') +
  ylab('Number of users') +
  scale_x_log10(breaks=seq(0, 2500, 300), limits=c(1, 2500))

fc_sqrt <- qplot(x = friend_count, data = pseudo_facebook, binwidth=.75
                  , color = I('black'), fill = I('blue')) +
  xlab('Number of friends (Square root transformation)') +
  ylab('Number of users') +
  scale_x_sqrt(breaks=seq(0, 5000, 100), limits=c(0, 2500))

grid.arrange(fc, fc_log10, fc_sqrt, nrow = 3)
```

Frequency polygons of number of likes by gender
```{r, echo=FALSE}
qplot(x = www_likes, y = ..count../sum(..count..), data = subset(pseudo_facebook, !is.na(gender))
      , geom = 'freqpoly', color = gender
      , xlab = 'Likes Count'
      , ylab = 'Number of Friends') + 
  scale_x_log10(breaks=seq(0,15000,1000), limits=c(1, 15000))
```

What's the males like count and who has more likes, males or females?
```{r, echo=FALSE}
by(pseudo_facebook$www_likes, pseudo_facebook$gender, sum)
```

Who has more friends, males or females?
Boxplot of friend count by gender
```{r, echo=FALSE}
qplot(x = gender, y = friend_count,data = subset(pseudo_facebook, !is.na(gender))
      , geom = 'boxplot') +
  coord_cartesian(ylim=c(0, 1000))
```
Numerical summary of friend count by gender
```{r, echo=FALSE}
by(pseudo_facebook$friend_count, pseudo_facebook$gender, summary)
```

Who initiated more friendships, males or females?
Boxplot of friendships initiated by gender
```{r, echo=FALSE}
qplot(x = gender, y = friendships_initiated
      , data = subset(pseudo_facebook, !is.na(gender))
      , geom = 'boxplot') +
  coord_cartesian(ylim = c(0:150))
```
Numerical summary of friendships initiated by gender
```{r, echo=FALSE}
by(pseudo_facebook$friendships_initiated, pseudo_facebook$gender, summary)
```

Create new logical variable to identify if an user has ever logged in using a mobile device
```{r}
pseudo_facebook$mobile_check_in <- ifelse(pseudo_facebook$mobile_likes > 0, 1, 0)
pseudo_facebook$mobile_check_in <- factor(pseudo_facebook$mobile_check_in)
summary(pseudo_facebook$mobile_check_in)
```
What percentage of users check in using mobile?
```{r, echo=FALSE}
sum(pseudo_facebook$mobile_check_in == 1)/length(pseudo_facebook$mobile_check_in)
```
  




