---
title: "Two Variables - Problem Set"
output: 
  html_document: 
    keep_md: yes
---

Import necessary libraries and data sets
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
library(dplyr) 
library(tidyr)
data(diamonds)
```

Setting seed for reproducibility
```{r}
set.seed(1234)
```

Scatterplot of price vs. x
```{r}
ggplot(data = diamonds, aes(x = x, y = price)) + 
  geom_point() 
```

* A strong non-linear (exponential) relationship between price and x
* Outliers appear when x < 3 and x > 9.5

Correlation analysis
```{r}
with(diamonds, cor.test(x, price))
with(diamonds, cor.test(y, price))
with(diamonds, cor.test(z, price))
```

Scatterplot of price vs. depth
```{r}
ggplot(data = diamonds, aes(x = x, y = depth)) + 
  geom_jitter(alpha=1/100, position = position_jitter(h = 0)) +
  scale_x_continuous(breaks=seq(0, 10, 2))
```

Correlation analysis of depth vs price
```{r}
with(diamonds, cor.test(depth, price))
```

Scatterplot of price vs. carat (Excluding top 1% percentile of both variables)
```{r}
ggplot(data = subset(diamonds, price > unname(quantile(price, .01)) | carat > unname(quantile(carat, .01))), aes(x = price, y = carat)) +
  geom_point()
```

Scatterplot of price vs. volume
```{r}
diamonds$volume = diamonds$x * diamonds$y * diamonds$z
ggplot(data = diamonds, aes(x = price, y = volume)) +
  geom_point()
```

Correlation analysis between price and volume
```{r}
with(subset(diamonds, volume > 0 & volume <= 800), cor.test(price, volume))
```

Scatterplot of price vs. volume (Excluding outliers)
```{r}
ggplot(data = subset(diamonds, volume > 0 & volume <= 800), aes(x = price, y = volume)) +
  geom_jitter(alpha=1/25, position = position_jitter(h = 0)) +
  geom_smooth(method = "lm", color = "red")
```

New diamonds dataframe arranged by clarity
```{r}
diamondsByClarity <- diamonds %>%
  group_by(clarity) %>% 
  summarise(mean_price = mean(price)
            , median_price = median(price)
            , min_price = min(price)
            , max_price = max(price)
            , n = n()) %>%
  arrange(clarity)
```

Bar plots of mean price by clarify and color
```{r}
diamonds_by_clarity <- group_by(diamonds, clarity)
diamonds_mp_by_clarity <- summarise(diamonds_by_clarity, mean_price = mean(price))

p1 <- ggplot(data = diamonds_mp_by_clarity, aes(x = clarity, y = mean_price)) + geom_col()

diamonds_by_color <- group_by(diamonds, color)
diamonds_mp_by_color <- summarise(diamonds_by_color, mean_price = mean(price))

p2 <- ggplot(data = diamonds_mp_by_color, aes(x = color, y = mean_price)) + geom_col()

grid.arrange(p1, p2, ncol=1)

```


